High-Dim Project

### 2014-12-18 highdim-paper/paper.tex
Added some bits on newsgroup data section

@@

>>>>

We experiment on the 20 newsgroups data, a collection of topically grouped 
email messages. 
Because we were having issues with speed, we selected 3 topics yielding
about 1600 documents evenly split.
To transform the documents into a vector representation 
suitable for our task, we first filter out any non alpha-numeric characters
and message headers. Words were then stemmed with the Porter stemmer. 
Words occuring fewer than 5 times were removed.
We finally convert each document into a vector of tf-idf weights.
The final dimensionality of this data was about 2,600.

@@

To create groups, we first clustered the documents using k-means clustering.
For each cluster we formed a feature group by taking the complete set of 
non-zero features for each document in the group.

We then used these feature groups to created a higher dimensional dataset of
duplicate features with non-overlapping groups, so that we could apply our
non-overlapping group lasso method to it.
